\documentclass[12pt]{article}
\usepackage{array}
\usepackage[a4paper, total={6in, 8in}]{geometry}

\title{Measures of Specialisation}

\begin{document}

\maketitle

\section{Metrics from the Literature}

\subsection{Proportion of Items}
\textbf{Source: }Ferrante et al 2015 \cite{ferrante:PLoSCB:2015} \\\\
\textbf{Description: } "Proportion of items retrieved by more than one [agent] over the total number of items retrieved".\\\\
\textbf{Formula: }\\
%
\[
\frac{R_{cooperative}}{R_{total}}
\]
where:
\begin{description}
\item[$R_{cooperative}$] is Resources retrieved by more than one agent
\item[$R_{total}$] is Total resources retrieved by the team
\end{description}
%
\textbf{Pros:}
\begin{itemize}
\item Simple
\end{itemize}
\textbf{Cons:}
\begin{itemize}
\item Agents can pick up and drop resources without contributing to their transportation e.g. Go to source, pick up and drop on the spot, transport another resource as a generalist.
\end{itemize}
\textbf{Thoughts:}\\
It's too easy for non-specialist strategies to look like specialisation.
I think this metric should be avoided if possible.

\subsection{Action Switches}
\textbf{Source: } Nitschke et al 2012 \cite{nitschke:SEC:2012} \\\\
\textbf{Description: } "The frequency with which the controller switches between executing distinct motor outputs (actions) during its lifetime".\\\\
\textbf{Formula: }\\
%
\[
\frac{A}{N}
\]
%
where:
\begin{description}
\item[$A$] is Action switches over an episode
\item[$N$] is Number of possible switches over an episode
\end{description}
\textbf{Pros:}
\begin{itemize}
\item Calculates an agent's specialisation rather than a team's. Can identify non-specialists on a team.
\end{itemize}
\textbf{Cons:}
\begin{itemize}
\item Only works if the dropper and collector strategies could be executed with just one action.
\end{itemize}
\textbf{Thoughts:}\\
This could be good if there's a way to adapt it to slope foraging.
Maybe something like number of area switches?
A pure collector shouldn't leave the nest and cache and a pure dropper shouldn't leave the source/slope.
But then, what if 

swap roles but stay specialised as a team
dropper that goes all the way down the slope, is that still a specialist?
How do I define specialisation, verbally?
Is there a way to define specialisation that is not unique to this application?
Is an agent specialised or is a team?

\subsection{•}

\textbf{Source: } \\\\
\textbf{Description: } \\\\
\textbf{Formula: }\\
%
%
\\\\
\textbf{Pros:}
\begin{itemize}
\item 
\end{itemize}
\textbf{Cons:}
\begin{itemize}
\item 
\end{itemize}
\textbf{Thoughts:}\\

\section{Metrics by Me}

\bibliographystyle{ieeetr} 
\bibliography{references}

\end{document}


